\documentclass{resume}

\usepackage[letterpaper]{geometry}
\usepackage{fontawesome}

\begin{document}
	\header{jeffrey}{xiao}{software engineer}

	\begin{sidebar}
		\section{contact}{blue}
			78 Alysha Way
			Maple, Ontario, Canada
			L6A0E5 
			~
			\iconentry{(647)-919-3171}{\faPhone}
			\iconentry{(905)-553-1136}{\faMobilePhone}
			~
			\iconentry{jeffrey.xiao1998@gmail.com}{\faEnvelope}
			\iconentry{jeffrey-xiao.github.io}{\faHome}
			\iconentry{github.com/jeffrey-xiao}{\faGithub}
			\iconentry{devpost.com/jeffreyxiao}{\faLink}
		\section{skills}{green}
			C++, Java, Python, HTML
			CSS, PHP, Javascript, jQuery
			ASP, Meteor, SQL, R, MATLAB
			Octave, LaTeX, Machine Learning
			Data Structures, Algorithms
		\section{certifications}{orange}
			Certified Java SE 6 Programmer
			Introduction to Logic by \emph{Princeton}
			Algorithms I \& II by \emph{Princeton}
			Introduction to Python by \emph{MIT \& HMC}
			Algorithms I \& II by \emph{Stanford}
			Machine Learning by \emph{Stanford}
			R Programming by \emph{Microsoft \& JHU}
		\section{programs}{red}
			\begin{entrylist}
				\leftentry{Shad Valley}{2015}
				\leftentry{Waterloo Unlimited}{2015}
			\end{entrylist}
		\section{awards}{purple}
			\begin{entrylist}
				\leftentry{Silver Medalist in Canadian Computing Olympiad}{2015}
				\leftentry{Platinum Division in USA Computing Olympiad}{2015}
				\leftentry{Duke of Edinburg Gold Standard}{2015}
				\leftentry{Chris Shaw Award in Computer Science}{2014}
				\leftentry{Michael Pincus Award in Mathematics}{2013}
			\end{entrylist}
	\end{sidebar}
	\begin{main}
		\vspace{10pt}%
		\section{\faBook}{education}{lightblue}
			\begin{entrylist}
				\rightentry%
				{Sep 2010 - Jun 2016}%
				{High School}%
				{University of Toronto Schools}%
				{}{}
			\end{entrylist}
		\section{\faBriefcase}{experience}{lightgreen}
			\begin{entrylist}
				\rightentry%
					{Nov 2015 - Current}%
					{Ivy Global}%
					{Toronto, Ontario}%
					{Web Developer}%
					{Developed a web application that displays SAT scores and statistics for mock exams in real time. Used ASP and SQL.}
				\rightentry%
					{Aug 2014}%
					{H.H. Angus and Associates}%
					{North York, Ontario}%
					{Intern}%
					{Researched floor and room designs for Centre Hospitalier de l'Universite de Montreal. Used CADD software to design an architectural model. Reported any discrepancies between 3D model and client specifications.}
				\rightentry%
					{Sep 2014 - Current}%
					{Creativity Through Arts}%
					{Markham, Ontario}%
					{Operations Executive}%
					{Responsible for the logistics and sponsorships behind events. Taught a web development course for high schoolers (\emph{creativitythrougharts.com/ctc}). Currently managing website and blog.}
				\rightentry%
					{Sep 2013 - Current}%
					{UTS Programming Club}%
					{Toronto, Ontario}%
					{President}%
					{Created information sheets and lectures on various topics in discrete mathematics. Cohosted a contest: \emph{dmoj.ca/contest/utsopen15}}
			\end{entrylist}
		\section{\faFolder}{projects}{lightpurple}
			\begin{entrylist}
				\rightentry%
					{Jan 2016}%
					{SwagMusic.js}%
					{Hack UofT}%
					{github.com/xelendt/swagmusic.js}%
					{3D model that dances to music. Built with WebGL and Web Audio API.}
				\rightentry%
					{Nov 2015}%
					{In The Loop}%
					{Hack Western}%
					{github.com/jeffrey-xiao/in-the-loop}%
					{AngularJS application and Python backend that aggregates current news information based on keywords in live time.}
				\rightentry%
					{Sep 2015}%
					{WhizBridge}%
					{Hack the North}%
					{github.com/jeffrey-xiao/WhizBridge}%
					{Web and iOS application that provides a buyer-oriented marketplace for tech support. Built with PHP and Swift.}
				\rightentry%
					{Aug 2015}%
					{Resistora}%
					{Tech Retreat}%
					{github.com/iburinoc/resistora}%
					{Android application that determines the resistance of various resistors using the camera and a custom image analysis algorithm.}
			\end{entrylist}	
	\end{main}
\end{document}