%!TEX TS-program = xelatex
\documentclass{resume}

\usepackage[letterpaper]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{hyperref}

\newfontfamily{\FA}{Font Awesome 5 Brands}

\makeatletter

\begin{document}
  \header%
    {jeffrey}%
    {xiao}%
    {\iterate{1-(647)-919-3171, \href{mailto:jeffrey.xiao@uwaterloo.ca}{jeffrey.xiao@uwaterloo.ca}}}%
    {\iterate{%
      \iconentry{\FA\symbol{"F015}}{\href{https://jeffreyxiao.me/}{jeffreyxiao.me}},%
      \iconentry{\FA\symbol{"F09B}}{\href{https://github.com/jeffrey-xiao/}{jeffrey-xiao}},%
      \iconentry{\FA\symbol{"F0E1}}{\href{https://www.linkedin.com/in/jeffreyxiao}{jeffreyxiao}}%
    }}%
  \begin{sidebar}
    \section{SKILLS}
      \subheader{Proficient}
        \iterate{Java, C, C++, C\#, Rust}
        \iterate{JavaScript, React, Node}
        \iterate{Python, Git, Linux}
      \subheader{Familiar}
        \iterate{Bash, Go, Scala}
    \section{AWARDS}
      \begin{itemize}[leftmargin=0.45cm, topsep=0.0cm]%
        \item[--] First, Greylock Hackfest \separator\emph{2017}
        \item[--] Second, MIT Battlecode \separator\emph{2017}
        \item[--] Fourth, ACM ICPC East Central North American Regionals \separator\emph{2016}
        \item[--] Bronze, International Olympiad in Informatics \separator\emph{2016}
        \item[--] Gold, Canadian Computing Olympiad \separator\emph{2016}
        \item[--] Silver, Canadian Computing Olympiad \separator\emph{2015}
        \item[--] Platinum Division, USA Computing Olympiad \separator\emph{2015}
      \end{itemize}%
    \section{CERTIFICATIONS}
      \begin{itemize}[leftmargin=0.45cm, noitemsep, topsep=0.0cm]%
        \item[--] Certified Java SE 6 Programmer
        \item[--] Algorithms I \& II, \emph{Princeton}
        \item[--] Machine Learning, \emph{Stanford}
        \item[--] R Programming, \emph{Microsoft \& JHU }
      \end{itemize}%
    \section{EDUCATION}
      \subheader{University of Waterloo}
      \color{tagText}Bachelor of Software Engineering
      \color{subTagText}2016 -- 2021 \separator\color{subTagText}Waterloo, Canada
      \color{bodyText}%
      \begin{itemize}[leftmargin=0.45cm, noitemsep, topsep=0.0cm]%
        \item[--] 93.15\% Cumulative Average
        \item[--] Dean's Honour List (3 Terms)
      \end{itemize}%
    \section{INTERESTS}
      \begin{itemize}[leftmargin=0.45cm, noitemsep, topsep=0.0cm]%
        \item[--] Distributed Systems
        \item[--] Data Infrastructure
        \item[--] Concurrent Computing
        \item[--] Database Internals
      \end{itemize}%
  \end{sidebar}
  \begin{main}
    \vspace{0.2cm}%
    \section{EXPERIENCE}
      \begin{entrylist}
        \rightentry%
          {Jan 2018 -- Apr 2018}%
          {datacoral Inc}%
          {San Francisco, California}%
          {Software Engineering Intern}%
          {\createlist%
            {%
              Scoped out, architected, and implemented highly scalable materialized views in %
              Redshift using Kinesis Data Streams, DynamoDB, and Lambda. %
            }%
            {%
              Used timelabel tags to represent the state of underlying data, update materialized %
              views when dependencies get updated, and handle schedule and view definition %
              changes. %
            }%
            {%
              Built critical APIs and migration scripts to launch a web application for monitoring %
              materialized views and data pipeline performance. %
            }%
          }
        \rightentry%
          {May 2017 -- Sep 2017}%
          {Yelp}%
          {San Francisco, California}%
          {Software Engineering Intern}%
          {\createlist%
            {%
              Explored and evaluated solutions for better client-side JS error reporting. %
            }%
            {%
              Implemented and rolled out infrastructure to process over 25 million errors every %
              month to over 20 services. %
            }%
            {%
              Modernized build pipeline and built tooling to migrate services from Google Closure %
              Library to ES6 and Webpack, and from npm to yarn. %
            }%
            {%
              Helped develop infrastructure and tooling to migrate services to React, including %
              server-side rendering of React components. %
            }%
          }
        \rightentry%
          {Nov 2015 -- Sep 2016}%
          {Ivy Global}%
          {Toronto, Ontario}%
          {Software Engineering Intern}%
          {\createlist%
            {%
              Led the development of a bubblesheet scanner and grader using convolutional neural %
              networks, and custom image processing algorithms to process blurred, tilted, and %
              imprecise images. %
            }%
            {%
              Developed an ASP web application that displays SAT scores and statistics for mock %
              exams in real-time. %
            }%
          }
      \end{entrylist}
    \section{PROJECTS}
      \begin{entrylist}
        \rightentry%
          {Rust, Distributed Systems}%
          {kademlia-dht-rs}%
          {Personal Project}%
          {\href{https://github.com/jeffrey-xiao/kademlia-dht-rs}{github.com/jeffrey-xiao/kademlia-dht-rs}}%
          {\createlist%
            {%
              A flexible implementation of Kademlia, a distributed hash table. %
            }%
            {%
              Used strict parallelism to efficiently send RPCs to probe nearby nodes. %
            }%
          }
        \rightentry%
          {Python, C++, Unity, TensorFlow}%
          {inSight}%
          {Greylock Hackfest}%
          {\href{https://goo.gl/Qy4TcJ}{goo.gl/Qy4TcJ}}%
          {\createlist%
            {%
              An interactive AR headset that uses machine learning and custom image %
              analysis algorithms to display information about the user's point of focus. %
            }%
            {%
              Applied gaze tracking to enable full control of headset via eye movement. %
            }%
            {%
              Used Bing and IoT technology to control home appliances and learn about surroundings %
              in an intuitive way. %
            }%
          }
        \rightentry%
          {Node, React, Android}%
          {Emergicare}%
          {Hack the North}%
          {\href{https://devpost.com/software/emergicare-hsup49}{devpost.com/software/emergicare-hsup49}}%
          {\createlist%
            {%
              Android background service that sends optimized GPS and network locations by text to %
              a specified number every time 911 is called. %
            }%
            {%
              Built an operator dashboard that supports routing of emergency vehicles simulated by %
              the Grand River Transit system. %
            }%
            {%
              \textit{Related blog post}: \color{lightred}\href{https://goo.gl/S5u1vr}{goo.gl/S5u1vr}%
            }%
          }
      \end{entrylist}
  \end{main}
\end{document}
